---
title: "Memo 3"
author: "Rameasa arna"
date: "10/7/2021"
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Import Data
```{r}
library(haven)
library(lattice)
library(foreign)
library(dplyr)
library(ggplot2)
library(descr)
library(tidyverse)
library(magrittr)

GSS <- read.dta("/Users/rameasaarna/Desktop/data 710/gss code book/GSS1972_2014v12.dta")
colnames(GSS, do.NULL = TRUE, prefix = "col")
```
##Should govt. improve standard of living
```{r}
GSS_Help_Poor = GSS%>%
         select(year, helppoor)%>%
        filter(helppoor <= 5)%>%
        mutate(helppoor = ifelse(helppoor == 2, 1, helppoor))%>% 
        mutate(helppoor = ifelse(helppoor == 4, 5, helppoor))%>% 
          mutate(helppoor = case_when(
            helppoor == 1 ~ "5 = SA TO A",
            helppoor == 3 ~ "3", 
            helppoor == 5 ~ "1 = SD TO D",
          ))
GSS_Help_Poor <- GSS_Help_Poor%>%
        mutate( 
                year.1 = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010")) 
  
#GSS_Help_Poor

#table(GSS_Help_Poor$helppoor, GSS_Help_Poor$helppoor)

Help_POOR = sjmisc::flat_table(GSS_Help_Poor, year.1, helppoor, margin = "row")
Help_POOR
```
```{r}
testing <- data.frame(Help_POOR)
testing$helppoor <- as.character(testing$helppoor)
testing <- testing%>%
  mutate(helppoor = ifelse(helppoor == "3", NA, helppoor), 
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helppoor) 
ggplot() + 
  geom_line(data=testing, aes(year.1, Freq, group = helppoor, col = helppoor))+ 
    labs(title = "Rspondents opinion on Should govt. improve standard of living ", x = "Years", y = "Proportions")+ 
  
  ylim(0, 1)
    
```

##graphing trends over time. 
```{r}
yearcat = c(1970, 1980, 1990, 2000, 2010)
racmarprop = c(.40, .32, .33, .26, .29)
Help_POOR_data= data.frame(yearcat, racmarprop)
#Help_POOR_data

ggplot()+
  geom_line(data = Help_POOR_data, aes(yearcat, racmarprop))+
  labs(title = "Trends in support for govt. should improve standard of living ", x = "Years", y = "Proportion")

```

##Should govt help black?
```{r}
GSS_Help_Black = GSS%>%
         select(year, helpblk)%>%
        filter(helpblk <= 5)%>%
        mutate(helpblk = ifelse(helpblk == 2, 1, helpblk))%>% 
        mutate(helpblk = ifelse(helpblk == 4, 5, helpblk))%>% 
          mutate(helpblk = case_when(
            helpblk == 1 ~ "5 = SA TO A",
            helpblk == 3 ~ "3", 
            helpblk == 5 ~ "1 = SD TO D",
          ))
GSS_Help_Black <- GSS_Help_Black%>%
        mutate( 
                year.1 = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010")) 
  

#GSS_Help_Black

#table(GSS_Help_Black$helpblk, GSS_Help_Black$helpblk)

Help_Black = sjmisc::flat_table(GSS_Help_Black, year.1, helpblk, margin = "row")
Help_Black
```
```{r}
testing <- data.frame(Help_Black)
testing$helpblk <- as.character(testing$helpblk)
testing <- testing%>%
  mutate(helpblk = ifelse(helpblk == "3", NA, helpblk), 
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helpblk) 
ggplot() + 
  geom_line(data=testing, aes(year.1, Freq, group = helpblk, col = helpblk))+ 
    labs(title = "Respondents opinion on Should govt help black? ", x = "Years", y = "Proportions")+
  ylim(0, 1)
    

```
##graphing trends over time. 
```{r}
yearcat = c(1970, 1980, 1990, 2000, 2010)
racmarprop = c(.25, .21, .20, .17, .18)
Help_Black_data= data.frame(yearcat, racmarprop)
#Help_Black_data

ggplot()+
  geom_line(data = Help_Black_data, aes(yearcat, racmarprop))+
  labs(title = "Trends in support for govt. should help black ", x = "Years", y = "Proportion")

```
##Favor law against interracial marriage
```{r}

#Do you think there should be laws against marriages between (negro/ black/ African- American) and whites?


GSS_Racmar = GSS%>%
         select(year, racmar)%>%
          mutate(racmar = ifelse(racmar == "yes", 1, 0),
                 year.2 = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010"))
#GSS_Racmar

#glimpse(GSS_Racmar)
```


# this table collapses the data by year categories and generates the proportion/ percentage supporting/ not supporting laws for each year category. for example; in 1972-82, 34% of the respondents supported the laws and 67% opposed them.
```{r}
#install.packages("sjmisc")
racmar.3 = sjmisc::flat_table(GSS_Racmar, year.2, racmar, margin = "row")
racmar.3
```


```{r}
testing <- data.frame(racmar.3)
testing$racmar <- as.character(testing$racmar)
testing <- testing%>%
  mutate( 
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
ggplot() + 
  geom_line(data=testing, aes(year.2, Freq, group = racmar, col = racmar))+ 
    labs(title = "Respondents opinion on interracial marriage ", x = "Years", y = "Proportions")+
  ylim(0, 1)
```

#graphing trends over time. 
```{r}
yearcat = c(1970, 1980, 1990, 2000, 2010)
racmarprop = c(.33, .24, .20, .12, .10)
racmar.2 = data.frame(yearcat, racmarprop)
racmar.2

ggplot()+
  geom_line(data = racmar.2, aes(yearcat, racmarprop))+
  labs(title = "Trends in support for Anti- miscegeny Laws, GSS 1972-2014", x = "Years", y = "Proportion")

```

## Difference due to discrimination

```{r}
GSS_Discri = GSS%>%
         select(year, racdif1)%>%
          mutate(racdif1 = ifelse(racdif1 == "yes", 1, 0),
                 year.2 = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010"))

#GSS_Discri

Discrimination = sjmisc::flat_table(GSS_Discri, year.2, racdif1, margin = "row")
Discrimination

```
```{r}
testing <- data.frame(Discrimination)
testing$racdif1 <- as.character(testing$racdif1)
testing <- testing%>%
  mutate( 
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
ggplot() + 
  geom_line(data=testing, aes(year.2, Freq, group = racdif1, col = racdif1))+ 
    labs(title = "Respondents opinion on Discrimination ", x = "Years", y = "Proportions")+
  ylim(0, 1)
```


#graphing trends over time. 
```{r}
yearcat = c(1970, 1980, 1990, 2000, 2010)
racmarprop = c(.41, .45, .42, .40, .37)
Discrimination_Data = data.frame(yearcat, racmarprop)
#Discrimination_Data

ggplot()+
  geom_line(data = Discrimination_Data, aes(yearcat, racmarprop))+
  labs(title = "Trends in support for (Negroes/Blacks/African-Americans) have worse jobs,income
       , and housing than white people due to discrimination, GSS 1972-2014", x = "Years", y = "Proportion")
```


##Difference due to inborn disability                       


```{r}
#Because most (Negroes/Blacks/African-Americans) have less in-born ability to learn?

GSS_less_ability = GSS%>%
         select(year, racdif2)%>%
          mutate(racdif2 = ifelse(racdif2 == "yes", 1, 0),
                 year.2 = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010"))

#GSS_less_ability

Inborn_Disability = sjmisc::flat_table(GSS_less_ability, year.2, racdif2, margin = "row")

Inborn_Disability



```

```{r}
testing <- data.frame(Inborn_Disability)
testing$racdif2 <- as.character(testing$racdif2)
testing <- testing%>%
  mutate( 
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
ggplot() + 
  geom_line(data=testing, aes(year.2, Freq, group = racdif2, col = racdif2))+ 
    labs(title = "Respondents opinion on (Negroes/Blacks/African-Americans) have worse jobs,
      income , and housing than white people because less in-born ability to learn", x = "Years", y = "Proportions")+
  ylim(0, 1)
```

###graphing trends over time. 
```{r}

yearcat = c(1970, 1980, 1990, 2000, 2010)
racmarprop = c(.26, .21, .18, .11, .10)
Inborn_Disability_data = data.frame(yearcat, racmarprop)
#Inborn_Disability_data
ggplot()+
  geom_line(data = Inborn_Disability_data, aes(yearcat, racmarprop))+
  labs(title = "Trends in support for (Negroes/Blacks/African-Americans) have worse jobs,
      income , and housing than white people because less in-born ability to learn , 
                                             GSS 1972-2014", x = "Years", y = "Proportion")
```




```{r Cleaning}
GSS_Extra <- GSS%>%
        select(year, helppoor, helpblk, racmar, racdif1, racdif2)%>%
        filter(helppoor <= 5)%>%
        filter(helpblk <= 5)

GSS_Extra <- GSS_Extra%>%
        mutate( 
                year = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010")) 
  

temp <- c("helppoor", "helpblk") 
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c(4), 5, x))
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c(2), 1, x))
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) factor(x, 
                                                  labels = c("5 = SA TO A",
                                                             "3", 
                                                             "1 = SD TO D")))
temp <- c("racmar", "racdif1", "racdif2") 
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c("yes"), 1, 0))

# Flat Table 
helppoor_table = sjmisc::flat_table(GSS_Extra, year, helppoor, margin = "row")
helpblk_table = sjmisc::flat_table(GSS_Extra, year, helpblk, margin = "row")
racmar_table = sjmisc::flat_table(GSS_Extra, year, racmar, margin = "row")
racdif1_table = sjmisc::flat_table(GSS_Extra, year, racdif1, margin = "row")
racdif2_table = sjmisc::flat_table(GSS_Extra, year, racdif2, margin = "row")

testing <- data.frame(helppoor_table)
testing$helppoor <- as.character(testing$helppoor)
testing <- testing%>%
  mutate(helppoor = ifelse(helppoor == "3", NA, helppoor),
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helppoor) 
testing_poor <- testing
testing_poor$helppoor <- paste0("poor ", testing_poor$helppoor)
testing_poor <- testing_poor%>% 
  rename("variable" = helppoor)

testing <- data.frame(helpblk_table)
testing$helpblk <- as.character(testing$helpblk)
testing <- testing%>%
  mutate(helpblk = ifelse(helpblk == "3", NA, helpblk), 
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helpblk) 
testing_black <- testing
testing_black$helpblk <- paste0("black ", testing_black$helpblk)
testing_black <- testing_black%>% 
  rename("variable" = helpblk)

testing <- data.frame(racmar_table)
testing$racmar <- as.character(testing$racmar)
testing <- testing%>%
  mutate(Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing_racemarriage <- testing
testing_racemarriage$racmar <- paste0("marriage ", testing_racemarriage$racmar)
testing_racemarriage <- testing_racemarriage%>% 
  rename("variable" = racmar)

testing <- data.frame(racdif1_table)
testing$racdif1 <- as.character(testing$racdif1)
testing <- testing%>%
  mutate(Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing_racdif1 <- testing
testing_racdif1$racdif1 <- paste0("racediff ", testing_racdif1$racdif1)
testing_racdif1 <- testing_racdif1%>% 
  rename("variable" = racdif1)


testing <- data.frame(racdif2_table)
testing$racdif2 <- as.character(testing$racdif2)
testing <- testing%>%
  mutate(Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing_racdif2 <- testing
testing_racdif2$racdif2 <- paste0("raceability ", testing_racdif2$racdif2)
testing_racdif2 <- testing_racdif2%>% 
  rename("variable" = racdif2)

total_table <- rbind(testing_racdif2, testing_racdif1, testing_racemarriage, testing_black, testing_poor)

all_opinions <- ggplot() + 
  geom_line(data=total_table, aes(year, Freq, group = variable, col = variable))+ 
    labs(title = "Respondents opinion on everything ", x = "Years", y = "Proportions")+
  ylim(0, 1)

```

```{r}
GSS_Extra <- GSS%>%
        select(year, helppoor, helpblk, racmar, racdif1, racdif2)%>%
        filter(helppoor <= 5)%>%
        filter(helpblk <= 5)

GSS_Extra <- GSS_Extra%>%
        mutate( 
                year = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010")) 
  

temp <- c("helppoor", "helpblk") 
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c(4), 5, x))
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c(2), 1, x))
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) factor(x, 
                                                  labels = c("5 = SA TO A",
                                                             "3", 
                                                             "1 = SD TO D")))
temp <- c("racmar", "racdif1", "racdif2") 
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c("yes"), 1, 0))

# Flat Table 
helppoor_table = sjmisc::flat_table(GSS_Extra, year, helppoor, margin = "row")
helpblk_table = sjmisc::flat_table(GSS_Extra, year, helpblk, margin = "row")
racmar_table = sjmisc::flat_table(GSS_Extra, year, racmar, margin = "row")
racdif1_table = sjmisc::flat_table(GSS_Extra, year, racdif1, margin = "row")
racdif2_table = sjmisc::flat_table(GSS_Extra, year, racdif2, margin = "row")

testing <- data.frame(helppoor_table)
testing$helppoor <- as.character(testing$helppoor)
testing <- testing%>%
  mutate(helppoor = ifelse(helppoor == "3", NA, helppoor),
         helppoor = ifelse(helppoor == "5 = SA TO A", NA, helppoor),
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helppoor) 
testing_poor <- testing
testing_poor$helppoor <- paste0("poor ", testing_poor$helppoor)
testing_poor <- testing_poor%>% 
  rename("variable" = helppoor)

testing <- data.frame(helpblk_table)
testing$helpblk <- as.character(testing$helpblk)
testing <- testing%>%
  mutate(helpblk = ifelse(helpblk == "3", NA, helpblk),
         helpblk = ifelse(helpblk == "5 = SA TO A", NA, helpblk),
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helpblk) 
testing_black <- testing
testing_black$helpblk <- paste0("black ", testing_black$helpblk)
testing_black <- testing_black%>% 
  rename("variable" = helpblk)

testing <- data.frame(racmar_table)
testing$racmar <- as.character(testing$racmar)
testing <- testing%>%
  mutate(Freq = Freq/100, 
         racmar = ifelse(racmar == "1", NA, racmar))
testing <- testing%>% 
  drop_na(racmar) 
testing$Freq <- round(testing$Freq, 2)
testing_racemarriage <- testing
testing_racemarriage$racmar <- paste0("marriage ", testing_racemarriage$racmar)
testing_racemarriage <- testing_racemarriage%>% 
  rename("variable" = racmar)

testing <- data.frame(racdif1_table)
testing$racdif1 <- as.character(testing$racdif1)
testing <- testing%>%
  mutate(Freq = Freq/100, 
         racdif1 = ifelse(racdif1 == "1", NA, racdif1))
testing <- testing%>% 
  drop_na(racdif1) 
testing$Freq <- round(testing$Freq, 2)
testing_racdif1 <- testing
testing_racdif1$racdif1 <- paste0("racediff ", testing_racdif1$racdif1)
testing_racdif1 <- testing_racdif1%>% 
  rename("variable" = racdif1)


testing <- data.frame(racdif2_table)
testing$racdif2 <- as.character(testing$racdif2)
testing <- testing%>%
  mutate(Freq = Freq/100, 
         racdif2 = ifelse(racdif2 == "1", NA, racdif2)) 
testing <- testing%>% 
  drop_na(racdif2) 
testing$Freq <- round(testing$Freq, 2)
testing_racdif2 <- testing
testing_racdif2$racdif2 <- paste0("raceability ", testing_racdif2$racdif2)
testing_racdif2 <- testing_racdif2%>% 
  rename("variable" = racdif2)

total_table <- rbind(testing_racdif2, testing_racdif1, testing_racemarriage, testing_black, testing_poor)

only_no_and_disagree <- ggplot() + 
  geom_line(data=total_table, aes(year, Freq, group = variable, col = variable))+ 
    labs(title = "All disagree-no opinons", x = "Years", y = "Proportions")+
  ylim(0, 1)

```

```{r}
GSS_Extra <- GSS%>%
        select(year, helppoor, helpblk, racmar, racdif1, racdif2)%>%
        filter(helppoor <= 5)%>%
        filter(helpblk <= 5)

GSS_Extra <- GSS_Extra%>%
        mutate( 
                year = case_when(
                   year >= 1972 & year <= 1982 ~ "1972-82",
                   year >= 1983 & year <= 1987 ~ "1983-87",
                   year >= 1988 & year <= 1992 ~ "1988-92",
                   year >= 1993 & year <= 1999 ~ "1993-99",
                   year >= 2000 & year <= 2010 ~ "2000-2010")) 
  

temp <- c("helppoor", "helpblk") 
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c(4), 5, x))
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c(2), 1, x))
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) factor(x, 
                                                  labels = c("5 = SA TO A",
                                                             "3", 
                                                             "1 = SD TO D")))
temp <- c("racmar", "racdif1", "racdif2") 
GSS_Extra[temp] <- lapply(GSS_Extra[temp], function(x) ifelse(x %in% c("yes"), 1, 0))

# Flat Table 
helppoor_table = sjmisc::flat_table(GSS_Extra, year, helppoor, margin = "row")
helpblk_table = sjmisc::flat_table(GSS_Extra, year, helpblk, margin = "row")
racmar_table = sjmisc::flat_table(GSS_Extra, year, racmar, margin = "row")
racdif1_table = sjmisc::flat_table(GSS_Extra, year, racdif1, margin = "row")
racdif2_table = sjmisc::flat_table(GSS_Extra, year, racdif2, margin = "row")

testing <- data.frame(helppoor_table)
testing$helppoor <- as.character(testing$helppoor)
testing <- testing%>%
  mutate(helppoor = ifelse(helppoor == "3", NA, helppoor),
         helppoor = ifelse(helppoor == "1 = SD TO D", NA, helppoor),
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helppoor) 
testing_poor <- testing
testing_poor$helppoor <- paste0("poor ", testing_poor$helppoor)
testing_poor <- testing_poor%>% 
  rename("variable" = helppoor)

testing <- data.frame(helpblk_table)
testing$helpblk <- as.character(testing$helpblk)
testing <- testing%>%
  mutate(helpblk = ifelse(helpblk == "3", NA, helpblk),
         helpblk = ifelse(helpblk == "1 = SD TO D", NA, helpblk),
         Freq = Freq/100) 
testing$Freq <- round(testing$Freq, 2)
testing <- testing%>% 
  drop_na(helpblk) 
testing_black <- testing
testing_black$helpblk <- paste0("black ", testing_black$helpblk)
testing_black <- testing_black%>% 
  rename("variable" = helpblk)

testing <- data.frame(racmar_table)
testing$racmar <- as.character(testing$racmar)
testing <- testing%>%
  mutate(Freq = Freq/100, 
         racmar = ifelse(racmar == "0", NA, racmar))
testing <- testing%>% 
  drop_na(racmar) 
testing$Freq <- round(testing$Freq, 2)
testing_racemarriage <- testing
testing_racemarriage$racmar <- paste0("marriage ", testing_racemarriage$racmar)
testing_racemarriage <- testing_racemarriage%>% 
  rename("variable" = racmar)

testing <- data.frame(racdif1_table)
testing$racdif1 <- as.character(testing$racdif1)
testing <- testing%>%
  mutate(Freq = Freq/100, 
         racdif1 = ifelse(racdif1 == "0", NA, racdif1))
testing <- testing%>% 
  drop_na(racdif1) 
testing$Freq <- round(testing$Freq, 2)
testing_racdif1 <- testing
testing_racdif1$racdif1 <- paste0("racediff ", testing_racdif1$racdif1)
testing_racdif1 <- testing_racdif1%>% 
  rename("variable" = racdif1)


testing <- data.frame(racdif2_table)
testing$racdif2 <- as.character(testing$racdif2)
testing <- testing%>%
  mutate(Freq = Freq/100, 
         racdif2 = ifelse(racdif2 == "0", NA, racdif2)) 
testing <- testing%>% 
  drop_na(racdif2) 
testing$Freq <- round(testing$Freq, 2)
testing_racdif2 <- testing
testing_racdif2$racdif2 <- paste0("raceability ", testing_racdif2$racdif2)
testing_racdif2 <- testing_racdif2%>% 
  rename("variable" = racdif2)

total_table <- rbind(testing_racdif2, testing_racdif1, testing_racemarriage, testing_black, testing_poor)

only_yes_and_agree <- ggplot() + 
  geom_line(data=total_table, aes(year, Freq, group = variable, col = variable))+ 
    labs(title = "All agree-yes opinons", x = "Years", y = "Proportions")+
  ylim(0, 1)
```

```{r}
all_opinions
only_no_and_disagree
only_yes_and_agree
```

